Less Funding, More Lecturers, and Fewer Professors: \\ \vspace{0.1cm} \Large{Stagnating State Funding for Higher Education and its Effect on Faculty at Public Universities}

### 2023-12-19 text/paper.tex
Writing updates, Table A1 needs re-do.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Title page
% Author
\author{Senan Hogan-Hennessy\thanks{
        For helpful comments I thank
        Levon Barseghyan,
        Francine Blau,
        Ryan Dycus,
        Ronald Ehrenberg,
        Michael Lovenheim,
        Jake Meyer,
        Douglas Miller,
        and Evan Riehl,
        as well as seminar participants at Cornell University for helpful discussion.} \\
    \vspace{0.1cm}
    Economics Department, Cornell University
}
% Title
\title{Less Funding, More Lecturers, and Fewer Professors: \\ \vspace{0.1cm}
    \Large{Stagnating State Funding for Higher Education and its Effect on Faculty at Public Universities}}
\date{This version: \today\thanks{
    This project's Github repository, with materials and anonymised data for replication, is available at 
    \url{https://github.com/shoganhennessy/state-funding-faculty}.
    Any comments or suggestions may be sent to me at \href{mailto:seh325@cornell.edu}{\nolinkurl{seh325@cornell.edu}}, or raised as an issue on the Github project.
    } \\ \vspace{0.1cm}
    \href{https://github.com/shoganhennessy/state-funding-faculty/blob/main/state-funding-faculty-2023.pdf}{Newest version available here.}
}
\rhead{\today}
\lhead{Less Funding, More Lecturers, and Fewer Professors.}
% Begin
\begin{document}
\maketitle
\thispagestyle{empty}
% Abstract
\begin{abstract}
    \noindent
    \input{sections/00-abstract.tex}
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Title page
% Author
\author{Senan Hogan-Hennessy\thanks{
        For helpful comments I thank
        Levon Barseghyan,
        Francine Blau,
        Ryan Dycus,
        Ronald Ehrenberg,
        Michael Lovenheim,
        Jake Meyer,
        Douglas Miller,
        and Evan Riehl.
        I thank seminar participants at Cornell University (2022, 2023) for helpful discussion.} \\
    \vspace{0.1cm}
    Economics Department, Cornell University
}
% Title
\title{Less Funding, More Lecturers, and Fewer Professors: \\ \vspace{0.1cm}
    \Large{Stagnating State Funding for Higher Education and its Effect on Faculty at Public Universities}}
\date{This version: \today\thanks{
    This project's Github repository, with materials and anonymised data for replication, is available at 
    \url{https://github.com/shoganhennessy/state-funding-faculty}.
    Any comments or suggestions may be sent to me at \href{mailto:seh325@cornell.edu}{\nolinkurl{seh325@cornell.edu}}, or raised as an issue on the Github project.
    } \\ \vspace{0.1cm}
    \href{https://github.com/shoganhennessy/state-funding-faculty/blob/main/state-funding-faculty-2023.pdf}{Newest version available here.}
}
\rhead{\today}
\lhead{Less Funding, More Lecturers, and Fewer Professors.}
% Begin
\begin{document}
\maketitle
\thispagestyle{empty}
% Abstract
\begin{abstract}
    \noindent
    \input{sections/00-abstract.tex}
\end{abstract}

### 2023-12-19 text/sections/00-abstract.tex
Writing updates, Table A1 needs re-do.

Public universities employ more lecturers than ever, while state funding for higher education has stagnated for over thirty years.
This paper shows falling state funding caused a substitution away from professors towards lecturers at US public universities, using a shift-share approach to instrument for state funding cuts relative to enrolment.
Universities employ $4.4$\% more lecturers per student following a $10$\% funding cut, relying less on professors by employing $1.4$\% fewer assistant professors and $1.2$\% fewer full professors per student.
Incumbent professors' salaries, promotion rate, and quit rate at Illinois universities are not affected by funding cuts, so that the substitution arose by limiting hiring of new tenure-track/tenured professors.
Stagnating public funding affects public universities as institutions, and likely contributed to deteriorating student outcomes at public universities since the 1990s.

>>>>

Public universities employ more lecturers and fewer professors than at any other point in the last thirty years, relative to student enrolment.
At the same time, state funding for higher education has stagnated.
This paper shows falling state funding caused a substitution away from professors towards lecturers at US public universities, using a shift-share approach to instrument for state funding cuts relative to enrolment.
Universities employ $4.4$\% more lecturers per student following a $10$\% funding cut, relying less on professors by employing $1.4$\% fewer assistant professors and $1.2$\% fewer full professors per student.
Incumbent professors' salaries, promotion rate, and quit rate at Illinois universities are not affected by funding cuts, so that the substitution arose by limiting hiring of new tenure-track/tenured professors.
Stagnating public funding affects faculty and public universities as institutions, likely contributing to worsening student outcomes at public universities since the 1990s.

### 2023-12-19 text/sections/01-introduction.tex
Writing updates, Table A1 needs re-do.

It is a priori unclear how faculty may be affected, as there are various margins that universities may to respond to funding cuts.
For example, university administrations may directly cut salaries or lay-off incumbent staff.
This happened in 2015 when the state of Illinois shut-down without setting a state budget, and the University of Illinois furloughed faculty thanks to the funding shortfall \citep{furlough2010}.
Similarly, faculty hiring committees are often cancelled or disrupted in response to funding cuts, meaning there are fewer faculty entering a department to replace those leaving.
On the other hand, some faculty positions may grow at universities in response to funding cuts.
Public universities do not restrict enrolment in response to funding cuts, so someone must teach the next year of students.
Lecturers can fill in teaching duties, at a lower cost for the universities than tenure-track professors, with less employment protections (e.g., no tenure).
But it is not certain that universities would hire more lecturers in the face of budget cuts; they may not hire any more instructional staff thanks to lack of resources.
Similarly, the universities may be limited from hiring more lecturers by competitive pressures from peer institutions \citep{hoxby2009changing,urquiola2020markets}, and instead focus on filling the funding gap by raising revenue from other sources, such as private funds or raising tuition.

In both analyses, I employ a shift-share instrument to identify changes in state funding for higher education.
State governments decide how to fund higher education by a complicated process which can be influenced by local economic conditions, changing state priorities, or informal lobbying from universities.
As such, state funding is not randomly assigned to universities and so it is necessary to employ an identification strategy to account for this.
The shift-share instrument identifies exogenous changes in state funding by exploiting differences in how much each university relied on state funding, interacted with state-wide changes in higher education funding --- following \cite{NBERw23736,NBERw27885}.
The approach relies on the insight that yearly state government budgets are decided without targetting individual universities for funding cuts, and exploits the fact that more reliant universities will be more affected by state-wide changes in higher education funding.
Additionally, I estimate effect of state funding on faculty multiple years after the initial funding cuts, using the local projections method thanks to time-series confounding between the funding shock and later years' level of state funding.\footnote{
    To the best of my knowledge, this is also the first paper to use the local projections method for a shift-share instrument, and to acknowledge the time-series confounding for shift-share IV models when the outcome is in future time periods.
}

In my national-level analysis (IPEDS), I find that state funding cuts cause public universities to substitute away from tenured and tenure-track professors towards lecturers.
A funding cut of \$1,000 per student leads to an average university employing 6 more lecturers;
in percentage terms, a funding cut of 10\% per student leads to a fall of 1.4\% in the number of assistant professors per student at a university, a fall of 1.2\% for tenured professors, and an increase in 4.4\% the number of lecturers per student.
Local projection estimates show that these effects linger for many years after the initial funding shock, showing that the effect is not isolated to the year of the funding cut. 
Over the same time period, state funding per student fell by around 35\%, professors per student fell by 9\%, and lecturers per student increased by 99\%.
These results show that falls in state funding explain around 53\% of the fall in professors per student,
% i.e. -(35 * 0.137) / -9
and 15.5\% of the rise in lecturers per student.
% ie., (35 * 0.437) / 99
In my analysis of all Illinois faculty (IBHED), I find that incumbent professors were not meaningfully affected, in terms of total salary, promotion rate, or rate of leaving the Illinois public university system.
Yet the hiring rate for new professors at public universities was negatively impacted by the state funding cuts.
This implies that faculty composition change arose by limiting the hiring of new professors; public universities increasingly hired contingent lecturers, and increasingly did not replace their retiring (or otherwise leaving) professors.
Suggestive evidence using data on cumulative hiring counts supports this hypothesis.

>>>>

It is a priori unclear how faculty may be affected, as there are various margins that universities may to respond to funding cuts.
For example, university administrations may directly cut salaries or lay-off incumbent staff.
This happened in 2015 when the state of Illinois shut-down without setting a state budget, and the University of Illinois furloughed faculty unable to pay salaries \citep{furlough2010}.
Similarly, faculty hiring committees are often cancelled or disrupted in response to funding cuts, meaning there are fewer faculty entering a department to replace those leaving.
On the other hand, some faculty positions may grow at universities in response to funding cuts.
Public universities do not restrict enrolment in response to funding cuts, so someone must teach the next year of students.
Lecturers can fill in teaching duties, at a lower cost for the universities than tenure-track professors, with less employment protections (e.g., no tenure).
But it is not certain that universities would hire more lecturers in the face of budget cuts; they may not hire any more instructional staff at all.
Similarly, the universities may be limited from hiring more lecturers by competitive pressures from peer institutions \citep{hoxby2009changing,urquiola2020markets}, and instead focus on filling the funding gap by raising revenue from other sources, such as private funds or raising tuition.

In both analyses, I employ a shift-share instrument to identify changes in state funding for higher education.
State governments decide how to fund higher education by a complicated process which can be influenced by local economic conditions, changing state priorities, or informal lobbying from universities.
As such, state funding is not randomly assigned to universities and so it is necessary to employ an identification strategy to account for this.
The shift-share instrument identifies exogenous changes in state funding by exploiting differences in how much each university relied on state funding, interacted with state-wide changes in higher education funding --- following \cite{NBERw23736,NBERw27885}.
The approach relies on the insight that yearly state government budgets are decided without targetting individual universities for funding cuts, and exploits the fact that more reliant universities will be more affected by state-wide changes in higher education funding.
Additionally, I estimate effect of state funding on faculty multiple years after the initial funding cuts, using the local projections method thanks to time-series confounding between the funding shock and later years' level of state funding.\footnote{
    To the best of my knowledge, this is also the first paper to use the local projections method for a shift-share instrument, and to acknowledge the time-series confounding for shift-share IV models when the outcome is in future time periods.
}
This approach allows me to test whether universities recover in years following the fundings cuts e.g., by resuming faculty hiring in later years.

In my national-level analysis (IPEDS), I find that state funding cuts cause public universities to substitute away from tenured and tenure-track professors towards lecturers.
A funding cut of \$1,000 per student leads to an average university employing 6 more lecturers;
in percentage terms, a funding cut of 10\% per student leads to a fall of 1.4\% in the number of assistant professors per student at a university, a fall of 1.2\% for tenured professors, and an increase in 4.4\% the number of lecturers per student.
Local projection estimates show that these effects linger for many years after the initial funding shock, showing that the effect is not isolated to the year of the funding cut. 
Over the same time period, state funding per student fell by around 35\%, professors per student fell by 9\%, and lecturers per student increased by 99\%.
These results show that falls in state funding explain around 53\% of the fall in professors per student,
% i.e. -(35 * 0.137) / -9
and 15.5\% of the rise in lecturers per student.
% ie., (35 * 0.437) / 99
In my analysis of all Illinois faculty (IBHED), I find that incumbent professors were not meaningfully affected, in terms of total salary, promotion rate, or rate of leaving the Illinois public university system.
Yet the hiring rate for new professors at public universities was negatively impacted by state funding cuts.
This implies that faculty substitution arose by limiting the hiring of new professors, which is supported by suggestive evidence on cumulative faculty hiring counts.
The substitution is persistent for up to ten years, meaning that universities did not resume professor hiring in years following the funding cut, making the substitution towards lecturers long-run.

### 2023-12-19 text/sections/03-concepts.tex
Writing updates, Table A1 needs re-do.

Universities can respond multiple ways to the falls in per student state funding.
\cite{NBERw23736} established that public universities who experienced state funding cuts did not fully off-set by raising tution, and cut total spending.
But it is not clear how these spending cuts went on to affect faculty --- or whether they did at all.

Wider changes in the American higher education sector may concurrently explain the trends in state funding and faculty substitition.
College selectivity changed drastically over the 21st century, where the top universities have become more selective while the average university less selective \citep{hoxby2009changing}.
While the average public university is becoming less selective, it is possible that their most productive or research-focused faculty more often move to more selective and prestigious (and often private) institutions, leaving public universities substituting toward lecturers over time.
This is one way in which the trends may be concurrent, but not causal.
I address this issue by using ssift-share instrument approach to isolate funding cuts that affected more funding-intensive universities, measuring the rate of substitution between lecturers and professors in response to yearly changes in state-wide funding.

Universities could respond to funding cuts by cutting faculty salaries, leading to high-performing faculty leaving the university.
Multiple universities passed a university-wide pay-cut for their faculty in response to state budget cuts around the 2008 recession, and Cornell University implemented a professor salary cut in 2020.\footnote{
    The Cornell University administration expected large fiscal squeezes in mid-2020, so imposed a faculty salary cut, and then returned the amount cut later in 2020 when the financial squeeze did not materialise.}
Funding cuts could also limit the amount public universities can offer to new faculty hires, leading to fewer or less accomplished faculty accepting these offers.\footnote{
    Faculty often consider their outside options in job decisions, considering offers for employment and/or promotion from multiple universities at the same time (see \citealt{blackaby2005} for an overview of faculty outside options).
    If public universities can only make low salary offers thanks to funding cuts, then they are less likely to land professors with multiple offers.
}
This effect may not be the same across faculty seniority; most universities hire more junior faculty each year, so that yearly hiring disruptions may disrupt the looser market for established full professors more than tighter market for assistant professors or lecturers.
While these factors make it unclear who will be affected most by funding cuts, there is one empirical fact worth noting: the average assistant or tenured professor earns more than double that of a lecturer (see \autoref{tab:illinois-summary}).
Secondly, lecturers are (by definition) granted shorter contracts than professors; assistant professors mostly have 5--6 year long contracts, full professors indefinite contracts (tenure), lecturers yearly or term-wise contracts.
If a public university's primary obligation is to teach, and they must fulfil this objective with fewer resources, then substitution away from tenure-track and tenured professors towards lecturers is rationalisable.

It is not clear when the effects of funding short-falls will be realised.
University departments often employ faculty on multiple-year contracts (e.g., the tenure contract), and individual professors' decisions to retire, move university, or leave academia are multiple-year commitments, so that it may take multiple years for university funding to change the faculty composition, or trickle down to faculty.
For example, university departments coordinate hiring in annual cycles, so that a budget short-fall in year $t$ may have no effect on the in-progress hiring committee and resulting hiring decisions, yet the hiring cycle in year $t+1$ may be postponed or cancelled in response.
As such, this paper investigates the dynamics of state funding shocks' effects on faculty, for the years following a state funding cut.

>>>>

Universities can respond multiple ways to the falls in per student state funding.
\cite{NBERw23736} established that public universities who experienced state funding cuts did not fully off-set by raising tuition, and cutting total spending.
But it is not clear how these spending cuts went on to affect faculty --- or whether they affected faculty at all.

Wider changes in the American higher education sector may concurrently explain the trends in state funding and faculty substitution.
College selectivity changed drastically over the 21st century, where the top universities have become more selective while the average university less selective \citep{hoxby2009changing}.
While the average public university is becoming less selective, it is possible that their most productive or research-focused faculty more often move to more selective and prestigious (and often private) institutions, leaving public universities substituting toward lecturers over time.
This is one way in which the trends may be concurrent, but not causal.
I address this issue by using shift-share instrument approach to isolate funding cuts that affected more funding-intensive universities, measuring the rate of substitution between lecturers and professors in response to yearly changes in state-wide funding.

Universities could respond to funding cuts by cutting faculty salaries, leading to more faculty leaving for jobs at other universities.
Multiple universities passed a university-wide pay-cut for their faculty in response to state budget cuts around the 2008 recession, and Cornell University implemented a professor salary cut in 2020.\footnote{
    The Cornell University administration expected large fiscal squeezes in mid-2020, so imposed a faculty salary cut, and then returned the amount cut later in 2020 when the financial squeeze did not materialise.}
Funding cuts could also limit the amount public universities can offer to new faculty hires, leading to fewer or less accomplished faculty accepting these offers.\footnote{
    Faculty often consider their outside options in job decisions, considering offers for employment and/or promotion from multiple universities at the same time (see \citealt{blackaby2005} for an overview of faculty outside options).
    If public universities can only make low salary offers thanks to funding cuts, then they are less likely to land professors with multiple offers.
}
This effect may not be the same across faculty seniority; most universities hire more junior faculty each year, so that yearly hiring disruptions may disrupt the looser market for established full professors more than tighter market for assistant professors or lecturers.
While these factors make it unclear who will be affected most by funding cuts, there is one empirical fact worth noting: the average Illinois assistant professor is paid $\$76,897$, tenured professor $\$109,283$, while lecturers earn $\$31,449$ more than double that of a lecturer (annual salary for 2010--2021 in 2021 USD, see \autoref{tab:illinois-summary}).
Secondly, lecturers are (by definition) granted shorter contracts than professors; assistant professors mostly work on 5--6 year long contracts, full professors on indefinite contracts (tenure), lecturers on yearly or term-wise contracts.
If a public university's primary obligation is to teach, and they must fulfil this objective with fewer resources, substituting away from tenure-track and tenured professors towards lecturers is rationalisable.

It is not clear when the effects of funding cuts will be realised.
University departments often employ faculty on multiple-year contracts (e.g., the tenure contract), and individual professors' decisions to retire, move university, or leave academia are multiple-year commitments, so that it may take multiple years for university funding to change the faculty composition, or trickle down to faculty.
For example, university departments coordinate hiring in annual cycles, so that a budget short-fall in year $t$ may have no effect on the in-progress hiring committee and resulting hiring decisions, yet the hiring cycle in year $t+1$ may be postponed or cancelled.
As such, this paper investigates the dynamics of state funding shocks' effects on faculty, for the years following a state funding cut.

### 2023-12-19 text/sections/04-empirical.tex
Writing updates, Table A1 needs re-do.

This paper identifies the effects of changes in state funding on faculty.
However, a university's state funding is not exogenous to state decisions for support of higher education, or exogenous to internal institutional decisions.
Instead, the state government and university administration undertake a complex process of allotting resources across multiple different priorities, including instruction, research, or between departments.
For example, it may be the case that a state government restricts funding for only its lowest performing universities in response to a budget shock, introducing a treatment selection-on-outcome threat to identification. 
Importantly, funding from a university's state government provides opportunity to address such endogeneity.

@@

I employ a local projections approach to model how faculty outcomes in years $t+k$ are affected by state funding in year $t$, for future years $k > 0$ \citep{jorda2005}.
The local projections method is an empirical model used to estimate dynamic treatment effects when the treatment is not binary, so that time-series confounding (i.e., treatment in time $t$ is correlated with treatment in time $t-1$) is present \citep{montiel2021local}.
This method estimates the effect of treatment $X_{i,t}$ on outcome $Y_{i, t+ k}$ in follow-on years $k > 0$, while accounting for the auto-correlation between the other years.\footnote{
    The funding shock has a persistent effect on state funding, multiple years after the initial funding shock, so that the instrument is similarly strong for the local projections method (see \autoref{fig:firststage-lp}).
}
Additionally, the approach accommodates use of an instrument for state funding \citep{olea2021inference}, so that I use the shift-share instument in local projections estimates as in the rest of the empirical analysis.
I present estimates in graphical form, where the $x$-axis represents the year relative to the funding shock (i.e., $x = 0$ represents the year of the state funding shock) and the $y$-axis represents the estimated effect of the funding shock on that year's outcome.\footnote{
    See \autoref{fig:count-lp} for the graphical format, and the corresponding note for further explanation.
}

>>>>

This paper identifies the effects of changes in state funding on faculty.
However, a university's state funding is not exogenous to state decisions for support of higher education, or exogenous to internal institutional decisions.
Instead, the state government and university administration undertake a complex process of allotting resources across multiple different priorities, including instruction, research, or between departments.
For example, it may be the case that a state government restricts funding for only its lowest performing universities in response to a budget shock, introducing a selection-on-outcomes threat to identification. 
Importantly, funding from a university's state government provides opportunity to address such endogeneity.

@@

I employ a local projections approach to model how faculty outcomes in years $t+k$ are affected by state funding in year $t$, for future years $k > 0$ \citep{jorda2005}.
The local projections method is an empirical model used to estimate dynamic treatment effects when the treatment is not binary, so that time-series confounding (i.e., treatment in time $t$ is correlated with treatment in time $t-1$) is present \citep{montiel2021local}.
This method estimates the effect of state funding $X_{i,t}$ on faculty outcomes $Y_{i, t+ k}$ in follow-on years $k > 0$, while accounting for the auto-correlation between state funding in surrounding years.\footnote{
    The funding shock has a persistent effect on state funding, multiple years after the initial funding shock, so that the instrument is similarly strong for the local projections method (see \autoref{fig:firststage-lp}).
}
Additionally, the approach accommodates the shift-share instrument for state funding \citep{olea2021inference}, so that I present instrumental variables estimates for this method as in the rest of the empirical analysis.

### 2023-12-19 text/sections/09-figures-tables.tex
Writing updates, Table A1 needs re-do.

\newpage
\begin{figure}[H]
    \centering
    \singlespacing
    \caption{Local Projection Estimates for Effect of State Funding on Faculty Count per Student at Universities, by Professor Group.}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Lecturers.}
        \includegraphics[width=\textwidth]{figures/lecturer-count-lp.png}
        \label{fig:lecturer-count-lp}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Assistant Professors.}
        \includegraphics[width=\textwidth]{figures/assistant-count-lp.png}
        \label{fig:assistant-count-lp}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Full Professors.}
        \includegraphics[width=\textwidth]{figures/full-count-lp.png}
        \label{fig:full-count-lp}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{All Professors.}
        \includegraphics[width=\textwidth]{figures/all-count-lp.png}
        \label{fig:all-count-lp}
    \end{subfigure}
    \label{fig:count-lp}
    \justify
    \footnotesize
    \textbf{Note}:
    These figures show the local projections estimates of regression specification \eqref{eqn:secondstage}, with the funding shock as an instrument for state funding.
    The unit of analysis is the university, and uses IPEDS data.
    The coefficient estimate is effect of state funding ($X_{i,t}$) on faculty count per student ($Y_{i,t}$), using the funding shock instrument ($Z_{i,t}$), while accounting for auto-correlation between different time periods --- i.e., between $X_{i,t}, X_{i,t-1}$ and $Y_{i,t}, Y_{i,t-1}$.
    These results use a $\log-\log$ specification, so the estimates are for the elasticity of professor count per student in a year $t+k$ with respect to state funding in year $t$, where years $k = 0, \hdots, 10$ are on the $x$-axis. 
    Standard errors are clustered at the state-year level.
\end{figure}

\newpage
\begin{figure}[H]
    \centering
    \singlespacing
    \caption{Local Projection Estimates for Effect of State Funding on Faculty Salaries per Student at Illinois Public Universities, by Professor Group.}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Lecturers.}
        \includegraphics[width=\textwidth]{figures/salaries-lecturer-illinois-lp-rolling.png}
        \label{fig:salaries-lecturer-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Assistant Professors.}
        \includegraphics[width=\textwidth]{figures/salaries-assistant-illinois-lp-rolling.png}
        \label{fig:salaries-assistant-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Full Professors.}
        \includegraphics[width=\textwidth]{figures/salaries-full-illinois-lp-rolling.png}
        \label{fig:salaries-full-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Administrator Professors.}
        \includegraphics[width=\textwidth]{figures/salaries-administrator-illinois-lp-rolling.png}
        \label{fig:salaries-administrator-illinois-lp-rolling}
    \end{subfigure}
    \label{fig:salaries-illinois-lp-rolling}
    \justify
    \footnotesize
    \textbf{Note}:
    These figures show the local projections estimates of regression specification \eqref{eqn:secondstage}, with the funding shock as an instrument for state funding.
    The unit of analysis is an individual faculty member (at an Illinois public university); funding data come from IPEDS, and faculty salaries from IBHED.
    The coefficient estimate is effect of state funding ($X_{i(j),t}$) on faculty salaries ($Y_{j,t}$), using the funding shock instrument ($Z_{i(j),t}$), while accounting for auto-correlation between different time periods --- i.e., between $X_{i(j),t}, X_{i(j),t-1}$ and $Y_{i(j),t}, Y_{i(j),t-1}$.
    These results use a $\log-\log$ specification, so the estimates are for the elasticity of faculty salaries student in a year $t+k$ with respect to state funding in year $t$, where years $k = 0, \hdots, 4$ are on the $x$-axis. 
    Standard errors are clustered at the university-year level, and \autoref{sec:iv-model-indiv} fully describes the differences in empirical specification when unit of analysis is an individual faculty member.
\end{figure}

>>>>

\newpage
\begin{figure}[H]
    \centering
    \singlespacing
    \caption{Local Projection Estimates for Effect of State Funding on Faculty Count per Student at Universities, by Professor Group.}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Lecturers.}
        \includegraphics[width=\textwidth]{figures/lecturer-count-lp.png}
        \label{fig:lecturer-count-lp}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Assistant Professors.}
        \includegraphics[width=\textwidth]{figures/assistant-count-lp.png}
        \label{fig:assistant-count-lp}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Full Professors.}
        \includegraphics[width=\textwidth]{figures/full-count-lp.png}
        \label{fig:full-count-lp}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{All Professors.}
        \includegraphics[width=\textwidth]{figures/all-count-lp.png}
        \label{fig:all-count-lp}
    \end{subfigure}
    \label{fig:count-lp}
    \justify
    \footnotesize
    \textbf{Note}:
    These figures show the local projections estimates of regression specification \eqref{eqn:secondstage}, with the funding shock shift-share as an instrument for state funding.
    The unit of analysis is the university, and uses IPEDS data.
    The $x$-axis represents the year relative to the funding shock (i.e., $x = 0$ represents the year of the state funding cut) and the $y$-axis represents the estimated effect in years relative to initial funding shock.
    The coefficient estimate is effect of state funding ($X_{i,t}$) on faculty count per student ($Y_{i,t}$), using the funding shock instrument ($Z_{i,t}$), while accounting for auto-correlation between different time periods --- i.e., between $X_{i,t}, X_{i,t-1}$ and $Y_{i,t}, Y_{i,t-1}$.
    These results use a $\log-\log$ specification, so the estimates are for the elasticity of professor count per student in a year $t+k$ with respect to state funding in year $t$, where years $k = 0, \hdots, 10$ are on the $x$-axis. 
    Standard errors are clustered at the state-year level.
\end{figure}

\newpage
\begin{figure}[H]
    \centering
    \singlespacing
    \caption{Local Projection Estimates for Effect of State Funding on Faculty Salaries per Student at Illinois Public Universities, by Professor Group.}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Lecturers.}
        \includegraphics[width=\textwidth]{figures/salaries-lecturer-illinois-lp-rolling.png}
        \label{fig:salaries-lecturer-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Assistant Professors.}
        \includegraphics[width=\textwidth]{figures/salaries-assistant-illinois-lp-rolling.png}
        \label{fig:salaries-assistant-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Full Professors.}
        \includegraphics[width=\textwidth]{figures/salaries-full-illinois-lp-rolling.png}
        \label{fig:salaries-full-illinois-lp-rolling}
    \end{subfigure}
    \begin{subfigure}[b]{0.495\textwidth}
        \centering
        \caption{Administrator Professors.}
        \includegraphics[width=\textwidth]{figures/salaries-administrator-illinois-lp-rolling.png}
        \label{fig:salaries-administrator-illinois-lp-rolling}
    \end{subfigure}
    \label{fig:salaries-illinois-lp-rolling}
    \justify
    \footnotesize
    \textbf{Note}:
    These figures show the local projections estimates of regression specification \eqref{eqn:secondstage}, with the funding shock shift-share as an instrument for state funding.
    The unit of analysis is an individual faculty member (at an Illinois public university); funding data come from IPEDS, and faculty salaries from IBHED.
    The $x$-axis represents the year relative to the funding shock (i.e., $x = 0$ represents the year of the state funding cut) and the $y$-axis represents the estimated effect in years relative to initial funding shock.
    The coefficient estimate is effect of state funding ($X_{i(j),t}$) on faculty salaries ($Y_{j,t}$), using the funding shock instrument ($Z_{i(j),t}$), while accounting for auto-correlation between different time periods --- i.e., between $X_{i(j),t}, X_{i(j),t-1}$ and $Y_{i(j),t}, Y_{i(j),t-1}$.
    These results use a $\log-\log$ specification, so the estimates are for the elasticity of faculty salaries student in a year $t+k$ with respect to state funding in year $t$, where years $k = 0, \hdots, 4$ are on the $x$-axis. 
    Standard errors are clustered at the university-year level, and \autoref{sec:iv-model-indiv} fully describes the differences in empirical specification when unit of analysis is an individual faculty member.
\end{figure}
